Synthesizing Symmetric Lenses

### 2018-06-05 papers/SymmetricLenses/main.tex
light editing and some comments through the end of section 2

\begin{abstract}
  Users commonly need to synchronize the data shared between formats, so edits
  to the data in one format gets propagated to the data in the other format.
  Manually writing the functions for these data synchronizers is tedious and
  error prone. Instead of manually writing these synchronizers, bidirectional
  languages can be used to express \emph{lenses}, groups of synchronization
  functions with guarantees about round-trip behavior. While these bidirectional
  languages help make programming these synthesizers less error-prone, they
  remain difficult to program in. Synthesizing bidirectional languages allows
  users to use lenses without manually programming them. Current
  synthesizers work only on the simplest types of lenses, when the two formats
  describe exactly the same data; this is often not the case.

@@

Unfortunately, writing such synchronizers is tedious and error prone.
Bidirectional languages ease the difficulty of writing such synchronizers, as a
single, well-typed program expresses a \emph{lens}, a group of conversion
functions guaranteed to satisfy round-tripping laws. However, bidirectional
languages are difficult to program in as well, often requiring users to permute
data in fiddly ways while satisfying the type system's complex unambiguity
constraints.

A better approach is to synthesize such conversion functions. Prior work on
synthesizing these functions assumes that all data fields present in one format
are present in the other, but this is not always true. Oftentimes, fields
present in one format are not present in the other: the commands scheduled to
run on Linux machines are typically different than the commands scheduled to run
on Windows machines; updated APIs can expose new information, or omit legacy
information; ICS files contain a URL field that Google Calendar CSV files do not
expose.

\emph{Symmetric lenses} formalize such conversion functions. However, these
symmetric lenses use external state for synchronization, in the form of a
\emph{complement}. These complements makes symmetric lenses difficult to use in
real-world synchronization tasks, as users must maintain the synchronized files
as well as the complements. The complement further complicates synthesis, as
input-output examples are no longer sufficient, instead edit sequences must be
provided.

To get around this, we reformulate symmetric lenses as \emph{simple symmetric
  lenses}. This reformulation does not use a complement, and only uses the files
that we aim to synchronize as state. We identify a property,
\emph{forgetfulness}, where if a symmetric lens can be written as a forgetful
symmetric lens, it can also be written a simple symmetric lens. We provide
combinators for building simple symmetric lenses on string data, and integrate
these combinators with Boomerang, a language for bidirectional programming on
strings. In Boomerang, and our extension to it, lens expressions are typed
between regular expressions, where the regular expressions describe the
synchronized data formats.

We provide a tool for synthesizing simple symmetric lenses. This tool
synthesizes symmetric lenses from a suite of input-output examples and a pair of
regular expressions describing the data formats. The synthesis algorithm uses
type-directed synthesis on the two regular expressions to synthesize a lens that
is well-typed between the provided regular expressions and satisfies the
provided input-output examples.

A primary difficulty is that there are a relatively many well-typed simple
symmetric lenses. As symmetric lenses permit data to be present in only one
format, for any data component there is now a choice: is this data only relevant
to this format and as such should be left unaligned (changes to this data are
not propagated to the other format), or is this data present in both formats and
as such should be aligned (changes to this data change are propagated to the
other format).

Operating under the assumption that users wish to align as much data as
possible, our algorithm tries to align as much data as the types and examples
allow. This task gets harder when there are more complex decisions involved. For
example, if I have two fields in one format, and one in the other, which field
in the first format should be aligned to the sole field of the second format? Or
would it be better for the field on the right to be aligneded to a mish-mash
of subcomponents from each field? To answer these questions, we develop a cost
metric for reasoning about which lens aligns the most information.

In particular, the cost of a lens is the expected number of bits required to
recover a string in one format when a synchronized string in the other format is
provided. In this model, bijective lenses have zero cost, and as more
information is left unsychronized, the cost is increased.

Our model for this is based on \emph{stochastic regular expressions}~\cite{?}.
Both a language and a probability distribution over that language is represented
by a stochastic regular expression, and we develop a way to syntactically infer
the expected information content (or \emph{entropy}) of an unambiguous regular
expression. This entropy is used to calculate the expected information content
to recover a string, when given a string it is synchronized to.

@@

Our first algorithm, \RXSearch, proposes candidate stochastic regular
expressions. These candidate stochastic regular expressions are generated by
traversing \emph{star semiring} equivalences on stochastic regular expressions.
These proposed stochastic regular expression pairs have equivalent languages and
probability distributions as the original ones: we prove the star-semiring
rewrites this synthesizer applies are sound rewrites on stochastic regular
expressions.

@@

We evaluate our algorithm on a benchmark suite consisting of synchronizing file
formats from configuration files, application-specific data storage files, and
data cleaning tasks. We find that our algorithm is able to synthesize all these
lenses in under 20 seconds.

@@

We motivate our problem with an extended example. Consider the previously
described example of keeping Linux and Windows scheduled jobs synchronized. In
this example, we describe keeping the file containing cron jobs (crontab) and a
Scheduled Tasks file (scheduled.job) synchronized. These are each formats
specifying when to run recurring tasks. For simplicity of description, we use a
minified version of each of these, with examples and regular expressions shown
in Figure~\ref{fig:minimized-representations}. Each file contains a list of
tasks set to run at specific times every hour. In both these formats, users can
either provide specific minutes they want to run the program during or they can
specify they want to run the program at every minute.

We wish for the jobs to be synchronized across our Windows and Linux devices.
However, the commands that need to be run are typically different for each
device. Paths are different in Windows and Linux, and while there is typically a
Windows equvialent for Linux commands, that equivalent command is not always
named the same thing. So while we want to be able to have the same number of
commands, with the commands running at the same times, we don't want to
align the actual commands that are run.

To synchronize these files, a few functions are needed. Two \emph{creates} are
needed; if a crontab is initialized, a synchronized Scheduled Tasks file should
also be created, and vice versa. Furthermore, \emph{puts} are needed; if a
crontab is updated, we should be able to combine it with a non-updated Scheduled
Tasks file, and output a new Scheduled Tasks file, synchronized to the updated
crontab. To have a simple symmetric lens is to have these required
synchronization functions. Formally, a simple symmetric lens between $X$ and $Y$
comprises 4 functions:
\begin{enumerate}
\item $\CreateR \OfType X \rightarrow Y$
\item $\CreateL \OfType Y \rightarrow X$
\item $\PutR \OfType X \rightarrow Y \rightarrow Y$
\item $\PutL \OfType Y \rightarrow X \rightarrow X$
\end{enumerate}
Furthermore, if a file is not edited, but is then resynchronized using a put
function, no data should be changed. To be a simple symmetric lens, one must
satisfy the following ``round-tripping'' laws, guaranteeing identity edits won't
change the file data.
\begin{gather}
  \tag{\CreatePutRL}
  \PutLOf{(\CreateROf{x})}{x} = x\\
  \tag{\CreatePutLR}
  \PutROf{(\CreateLOf{y})}{y} = y\\
  \tag{\PutRL}
  \PutLOf{(\PutROf{x}{y})}{x} = x\\
  \tag{\PutLR}
  \PutROf{(\PutLOf{y}{x})}{y} = y
\end{gather}

@@

or(ins("<Tasks></Tasks>"),nonempty_task_map) : crontab $\Leftrightarrow$ scheduled_job
\end{lstlisting}
  \caption{A lens, written in our language for building simple symmetric lenses
    on string data, that synchronizes crontab files and Scheduled Task files.
    Note that we can annotate our lenses with types, to confirm the lens
    operates on the languages of the regular expressions.}
  \label{fig:example_lens}
\end{figure}

@@

\subsection{Synthesizing Symmetric Lenses}
To alleviate these difficulties, we wish to synthesize symmetric lenses from
types and examples. Given a pair of regular expressions and a set of
input-output examples, we want to synthesize a symmetric lens expression that is
typed between the regular expression pair, and satisfies the input/output
examples. In this example, we wish to synthesize a lens from \lstinline{crontab}
and \lstinline{scheduled_job}, using the strings in
Figure~\ref{fig:minimized-representations} as an input-output example for
\CreateR.

@@

But what is the best satisfying lens? We think the best satisfying lens is the
one that aligns as much data as is permitted by the type system and the
examples. More formally, we wish to minimize the expected number of bits
required to recover data in one format from a synchronized string in the other.
The expected number of bits is a well known concept in information theory: the
expected number of bits of a data source is the \emph{entropy} of that data
source.

The entropy of a data source is based on the probability distribution of that
data source. Given a set $S$, and a probability distribution over that set $P
\OfType S \rightarrow \Reals$, the entropy of the $(S,P)$ pair is $-\Sigma_{s\in
  S}P(s)\Log_2P(s)$. While we have ways of expressing sets of strings (with
regular expressions), we do not have probability distributions. In this work, we
express these probability distributions jointly with the language through
\emph{stochastic regular expressions}, regular expressions annotated with
probabilities. In this work, we guess a reasonable probability distribution from
the syntax, though if users manually provided stochastic regular expressions, or
large suite of data in the formats through which we could learn the annotations,
we could instead use that.

With sets and probability distributions, we can find the expected number of bits
required to recover one string from a synchronized string. This expected value
is the conditional entropy of the stochastic regular expression ($\Regex$) given
another stochastic regular expression ($\RegexAlt$), and a lens that shows which
strings are synchronized with which ($\Lens$). We aim to find the lens that
minimizes the sum of that entropy with the conditional entropy of $\RegexAlt$
given $\Regex$ and $\Lens$. Now that we have a notion of best, we need a way to
search for that best lens.

Our overall approach involves two communicating synthesizers: one (\RXSearch)
that proposes regular expression pairs, semantically but not syntactically
equivalent to the originals; one (\GreedySynth) that tries to find the best lens
within a class of lenses, characterized by such regular expression pairs. Given
two regular expressions, \GreedySynth can quickly search through the class of
lenses that can be typed between them, where all instances of type equivalence
involve no star equivalences. For example, consider the lens shown in
Figure~\ref{fig:example_lens}. This lens would \emph{not} be in the class
characterized by \lstinline{crontab} and \lstinline{scheduled_job}, as that
typing derivation requires unrolling \lstinline{xml_task$^*$} within
\lstinline{scheduled_job} into \lstinline{"" | (xml_task . xml_task$^*$)}.

@@

Critically for this work, \GreedySynth efficiently searches for one of the best
lenses in a class of lenses, characterized by a stochastic regular expression
pair. \GreedySynth works by searching through a smaller search space. First,
\GreedySynth converts the provided stochastic regular expression pair into a
\emph{stochastic DNF regular expression} pair. Then, the algorithm uses the
syntax of the DNF regular expression pair to greedily find a highly normalized
version of a simple symmetric lens, a \emph{symmetric DNF lens}. Finally, this
symmetric DNF lens is converted into a simple symmetric lens. DNF Lenses include
neither a composition operator nor a type equivalence rule. Unlike simple
symmetric lenses, for which a single lens term is typed between many possible
regular expression pairs, each DNF lens is only typed between a single regular
expression pair. The relationship between DNF lens syntax and DNF regular
expression syntax is incredibly tight, permitting an incredibly efficient
synthesis algorithm for DNF lenses from DNF regular expressions.

Our strategy involving communicating synthesizers permits both a way of
enumerating classes and efficiently searching through them, but it poses a
problem: unless we find a lens with no cost, other lens classes may contain
better lenses. While we may have found a great lens between two regular
expressions, a different regular expression pair may provide an even better
lens. There may be a great lens in the class characterized by
\lstinline{crontab} and \lstinline{scheduled_job}, but it is not the the
intended lens shown in Figure~\ref{fig:example_lens}. However, there is a
tension, we want to find a good lens, but we also want to give quick feedback to
the user. After finding the lens in Figure~\ref{fig:example_lens}, we dont want
the algorithm to spend much longer searching for better lenses.

We address this by keeping running track of the best lens found thus far, and
eventually cutting the proposal-synthesis loop short. Before proposing new
types, the regular expression generator, \RXSearch, evaluates whether it should
continue proposing regular expression pairs, or whether it is content with the
current best. For a given regular expression pair, \RXSearch looks at the number
of rewrite rules performed on the pair, and identifies how many pairs with
involving the same number of rewrites may be proposed. If there are a large
number of pairs that can be proposed with that many rewrites, or the current
lens is very well synchronized, \RXSearch does not propose that pairs. In this
way, \RXSearch will continue searching for better lenses, but does not tackle
huge search spaces unless it needs to. In this way, the algorithm can provide
lenses quickly to the users, which users can refine with additional examples.
% end overview

>>>>

\begin{abstract}
\saz{This abstract too long and doesn't get to the point quickly enough. We
  should tighten it up considerably.}
  Users commonly need to synchronize the data shared between formats, so edits
  to the data in one format gets propagated to the data in the other format.
  Manually writing the functions for these data synchronizers is tedious and
  error prone. Instead of manually writing these synchronizers, bidirectional
  languages can be used to express \emph{lenses}, groups of synchronization
  functions with guarantees about round-trip behavior. While these bidirectional
  languages help make programming these synthesizers less error-prone, they
  remain difficult to program in. Synthesizing bidirectional languages allows
  users to use lenses without manually programming them. Current
  synthesizers work only on the simplest types of lenses, when the two formats
  describe exactly the same data; this is often not the case.

@@

Unfortunately, writing such synchronizers is tedious and error
prone.\saz{``tedious and error prone'' is such a PL clich\'{e}, can we do better?}
Bidirectional languages ease the difficulty of writing such synchronizers, because a
single, well-typed program expresses a \emph{lens}---a group of conversion
functions guaranteed to satisfy round-tripping laws. However, bidirectional
languages are themselves difficult to program in, often requiring users to permute
data in fiddly ways while satisfying the type system's complex unambiguity
constraints.

A better approach is to \emph{synthesize} such conversion functions. However,
prior work on synthesizing lenses assumes a bijection between the source and
target, which is a severe limitation in practice. Oftentimes, fields present in
one format are not present in the other: the commands scheduled to run on Linux
machines are typically different than the commands scheduled to run on Windows
machines; updated APIs can expose new information, or omit legacy information;
ICS files contain a URL field that Google Calendar CSV files do not expose.

\emph{Symmetric lenses} \saz{citations?} formalize this richer class of
non-bijective conversion functions by using additional state, called the
\emph{complement}, to help with synchronization. While increasing
expressiveness, the existence of the complement makes symmetric lenses difficult
to use in real-world synchronization tasks, because users\saz{lens developers?
  lens programs?}  must maintain the synchronized files as well as the
complements. The complement further complicates synthesis, because input-output
examples no longer suffice; instead edit sequences must be provided.

In this paper, we reformulate \saz{this sounds like they may be of the same
  expressiveness, but perhaps we mean to ``constrain'' symmetric lenses?}
symmetric lenses as \emph{simple symmetric lenses}. This reformulation does not
use a complement, and only uses the files that we aim to synchronize as
state. We identify a property, \emph{forgetfulness}, that identifies the subset
of symmetric lenses that can be written as simple symmetric lenses. We provide
combinators for building simple symmetric lenses on string data, and integrate
these combinators with Boomerang, a language for bidirectional programming on
strings. In Boomerang, and our extension to it, lens expressions are typed
between regular expressions, where the regular expressions describe the
synchronized data formats.

We provide a tool for synthesizing simple symmetric lenses when given a suite of
input-output examples and a pair of regular expressions describing the data
formats. The synthesis algorithm uses type-directed synthesis on the two regular
expressions to synthesize a lens that is well-typed between the provided regular
expressions and satisfies the provided input-output examples.

\saz{This paragraph is hard to follow --- maybe introduce $\ell : S
  \Leftrightarrow T$ and use the names $S$ and $T$?}
A primary difficulty is that there are a relatively many well-typed simple
symmetric lenses. As symmetric lenses permit data to be present in only one
format, for any data component there is now a choice: is this data only relevant
to this format and as such should be left unaligned (changes to this data are
not propagated to the other format), or is this data present in both formats and
as such should be aligned (changes to this data change are propagated to the
other format).

Operating under the assumption that users wish to align as much data as
possible, our algorithm tries to align as much data as the types and examples
allow. This task gets harder when there are more complex decisions involved. For
example, if there are two fields in one format, and one in the other, which field
in the first format should be aligned to the sole field of the second format? Or
would it be better for the field on the right to be aligneded to a mish-mash
of subcomponents from each field? To answer these questions, we develop a cost
metric for reasoning about which lens aligns the most information.

In particular, the \emph{cost} of a lens is the expected number of bits required to
recover a string in one format when a synchronized string in the other format is
provided. In this model, bijective lenses have zero cost, and as more
information is left unsychronized, the cost is increased.

Our model is based on \emph{stochastic regular expressions}~\cite{?}, which
represent both a language and a probability distribution over that language
simultaneously.  We develop a way to syntactically infer the expected
information content (or \emph{entropy}) of an unambiguous regular
expression. This entropy is used to calculate the expected information content
to recover a string, when given a string it is synchronized with.

@@

Our first algorithm, \RXSearch, proposes candidate stochastic regular
expressions. These candidate stochastic regular expressions are generated by
traversing \emph{star semiring} equivalences on stochastic regular expressions.
These proposed stochastic regular expression pairs have equivalent languages and
probability distributions as the original ones: we prove that the star-semiring
rewrites this synthesizer applies are sound rewrites on stochastic regular
expressions.

@@

We evaluate our algorithm on a benchmark suite consisting of synchronizing file
formats from configuration files, application-specific data storage files, and
data cleaning tasks. We find that our algorithm is able to synthesize all
\saz{or each?}  of these lenses in under 20 seconds.

@@

We motivate our problem with an extended example. Consider the previously
described goal of keeping Linux cron jobs (crontab) and Windows Scheduled Tasks
(scheduled.job) synchronized. These are each formats specifying when to run
recurring tasks. For the sake of exposition, we use simplified versions crontab
and scheduled.job formats, with examples and corresponding regular expressions
shown in Figure~\ref{fig:minimized-representations}. Each file contains a list
of tasks set to run at specific times every hour. In both formats, users
can either provide specific minutes at which they want the program to run, or they
can specify that the program should run at every minute.

We wish for the jobs to be synchronized across our Windows and Linux devices.
However, the commands that need to be run are typically different for each
device. Paths are different in Windows and Linux, and, while there is typically a
Windows equvialent for a Linux command, that equivalent command is not always
named the same thing. So, while we want to be able to have the same number of
commands, with the commands running at the same times, we don't want to
align the actual commands that are run.

\saz{Perhaps we should explicitly say here that we are trying to define a lens,
  or describing the functions that a lens provides.}
To synchronize these files, a few functions are needed. Two \emph{creates}
\saz{we haven't introduced ``create'' as a noun yet.} are
needed; if a crontab is initialized, a synchronized Scheduled Tasks file should
also be created, and vice versa. Furthermore, \emph{puts} are needed; if a
crontab is updated, we should be able to combine it with a non-updated Scheduled
Tasks file, and output a new Scheduled Tasks file, synchronized to the updated
crontab. To have a simple symmetric lens is to have these required
synchronization functions. Formally, a simple symmetric lens between $X$ and $Y$
comprises 4 functions:
\begin{enumerate}
\item $\CreateR \OfType X \rightarrow Y$
\item $\CreateL \OfType Y \rightarrow X$
\item $\PutR \OfType X \rightarrow Y \rightarrow Y$
\item $\PutL \OfType Y \rightarrow X \rightarrow X$
\end{enumerate}
Furthermore, if a file is not edited, but is then resynchronized using a put
function, no data should be changed. To be a simple symmetric lens, one must
satisfy the following ``round-tripping'' laws, guaranteeing identity edits won't
change the file data.
\begin{gather}
  \tag{\CreatePutRL}
  \PutLOf{(\CreateROf{x})}{x} = x\\
  \tag{\CreatePutLR}
  \PutROf{(\CreateLOf{y})}{y} = y\\
  \tag{\PutRL}
  \PutLOf{(\PutROf{x}{y})}{x} = x\\
  \tag{\PutLR}
  \PutROf{(\PutLOf{y}{x})}{y} = y
\end{gather}

@@

or(ins("<Tasks></Tasks>"),nonempty_task_map) : crontab $\Leftrightarrow$ scheduled_job
\end{lstlisting}
  \caption{A lens, written in our language for building simple symmetric lenses
    on string data, that synchronizes crontab files and Scheduled Task files.
    Note that we can annotate our lenses with types, to confirm the lens
    operates on the languages of the regular expressions.\saz{Say something
      about the possibility of synthesizing this lens?}}
  \label{fig:example_lens}
\end{figure}

@@

\subsection{Synthesizing Symmetric Lenses}

To alleviate these difficulties, we wish to synthesize symmetric lenses---given
a pair of regular expressions and a set of input-output examples, we want to
find a symmetric lens expression that is typed between the regular expression
pair, and satisfies the input/output examples. In this example, we wish to
synthesize a lens from \lstinline{crontab} and \lstinline{scheduled_job}, using
the strings in Figure~\ref{fig:minimized-representations} as an input-output
example for \CreateR.

@@

But what is the best satisfying lens? Here, we take the view that the best satisfying lens is the
one that aligns as much data as is permitted by the type system and the
examples. More formally, we wish to minimize the expected number of bits
required to recover data in one format from a synchronized string in the other.
The expected number of bits is a well known concept in information theory: the
\emph{entropy} of that data source.

The entropy of a data source is based on the probability distribution of that
data source. Given a set $S$, and a probability distribution over that set $P
\OfType S \rightarrow \Reals$, the entropy of the $(S,P)$ pair is $-\Sigma_{s\in
  S}P(s)\Log_2P(s)$. While we have ways of expressing sets of strings (with
regular expressions), we do not have probability distributions. Here, we
express these probability distributions jointly with the language through
\emph{stochastic regular expressions}, regular expressions annotated with
probabilities. Our algorithm guesses a reasonable probability distribution from
the syntax, though if users manually provided stochastic regular expressions, or
a large suite of data in the formats through which we could learn the annotations,
we could instead use that.

With sets and probability distributions, we can find the expected number of bits
required to recover one string from a synchronized string. This expected value
is the conditional entropy of the stochastic regular expression ($\Regex$) given
another stochastic regular expression ($\RegexAlt$), and a lens that shows which
strings are synchronized with which ($\Lens$). We aim to find the lens that
minimizes the sum of that entropy with the conditional entropy of $\RegexAlt$
given $\Regex$ and $\Lens$.

Now that we have a notion of best, we need a way to
search for that best lens.
Our overall approach involves two communicating synthesizers: one (\RXSearch)
that proposes regular expression pairs, semantically but not syntactically
equivalent to the originals; one (\GreedySynth) that tries to find the best lens
within a class of lenses, characterized by such regular expression pairs. Given
two regular expressions, \GreedySynth can quickly search through the class of
lenses that can be typed between them, where all instances of type equivalence
involve no star equivalences. For example, consider the lens shown in
Figure~\ref{fig:example_lens}. This lens would \emph{not} be in the class
characterized by \lstinline{crontab} and \lstinline{scheduled_job}, as that
typing derivation requires unrolling \lstinline{xml_task$^*$} within
\lstinline{scheduled_job} into \lstinline{"" | (xml_task . xml_task$^*$)}.

@@

Critically for this work, \GreedySynth efficiently searches for one of the best
lenses in a class of lenses, characterized by a stochastic regular expression
pair. \GreedySynth works by searching through a smaller search space. First,
\GreedySynth converts the provided stochastic regular expression pair into a
\emph{stochastic DNF regular expression} pair. Then, the algorithm uses the
syntax of the DNF regular expression pair to greedily find a highly normalized
version of a simple symmetric lens, a \emph{symmetric DNF lens}. Finally, this
symmetric DNF lens is converted into a simple symmetric lens. DNF Lenses include
neither a composition operator nor a type equivalence rule. Unlike simple
symmetric lenses, for which a single lens term is typed between many possible
regular expression pairs, each DNF lens is typed only between a single regular
expression pair. The relationship between DNF lens syntax and DNF regular
expression syntax is very tight, permitting an efficient
synthesis algorithm for DNF lenses from DNF regular expressions.

Our strategy involving communicating synthesizers permits both a way of
enumerating classes and efficiently searching through them, but it poses a
problem: when do we stop? While we may have found a great lens between two regular
expressions, a different regular expression pair may provide an even better
lens. Moreover, we may find a great lens characterized by
\lstinline{crontab} and \lstinline{scheduled_job} that is not the
desired lens shown in Figure~\ref{fig:example_lens}.  The
tension is that we want to find a good lens, but we also want to give quick feedback to
the user. After finding the lens in Figure~\ref{fig:example_lens}, we dont want
the algorithm to spend much longer searching for better lenses.

\saz{The following is hard to follow}
We address this issue by keeping track of the best lens found thus far, and
eventually cutting the proposal-synthesis loop short. Before proposing new
types, the regular expression generator, \RXSearch, evaluates whether it should
continue proposing regular expression pairs, or whether it is content with the
current best. For a given regular expression pair, \RXSearch looks at the number
of rewrite rules performed on the pair, and identifies how many pairs
involving the same number of rewrites may be proposed. If there are a large
number of pairs that can be proposed with that many rewrites, or the current
lens is very well synchronized, \RXSearch stops. In this
way, \RXSearch will continue searching for better lenses, but does not tackle
huge search spaces unless it needs to. In this way, the algorithm can provide
lenses quickly to the users, which users can refine with additional examples.
% end overview
